Quality Definitions of Qualities

### 2020-01-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
update Productivity
update completeness

Thus, we can improve the productivity of the software process by increasing its
outputs, decreasing its inputs, or both. However, this means that we need to
provide meaningful definitions of the inputs and outputs of the software
process. \wss{Where did this definition come from?  Is this all from Boehm?
  This is quite a long quote.  We might actually want to paraphrase.}

@@

\begin{defn}
  The degree to which a full implementation of the required functionality has
  been achieved \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
  \wss{Ao, if this is from McCall, we should just cite the primary source and
    remove the Van Vliet reference.} \pmi{McCall's definition verbatim: Those attributes of the software that provide full implementation of the functions required.}
\end{defn}

>>>>

Thus, we can improve the productivity of the software process by increasing its
outputs, decreasing its inputs, or both. However, this means that we need to
provide meaningful definitions of the inputs and outputs of the software
process. \wss{Where did this definition come from?  Is this all from Boehm?
  This is quite a long quote.  We might actually want to paraphrase.}
\ad{all from Boehm. I feel the best way is deleting everything after the 
equation}

@@

\begin{defn}
  Those attributes of the software that provide full implementation of the 
  functions required. \citep{McCallEtAl1977}. \wss{Ao, if this is from McCall, 
  we should just cite the primary source and remove the Van Vliet reference.} 
  \pmi{McCall's definition verbatim: Those attributes of the software that 
  provide full implementation of the functions required.} \ad{Originally added 
  by someone else so I didn't have access to the book. But now it's available 
  and I double checked, Peter got it accurately.}
\end{defn}
